Draft genomes of the three northern hemisphere blue mussel lineages: North and South European \emph{Mytilus edulis} and Mediterranean \emph{Mytilus galloprovincialis}.

### 2022-06-24 manuscript/ms_genomes.tex
update

@@

>>>>

We introduce here newly assembled genomes from three lineages of the \textit{Mytilus} species complex.
With a limited budget of $\sim$3000€ per genome, we managed to produce draft genomes of enough quality to be useful
in applications such as population genomics and genetics.
The method of 10X chromium pseudo-long reads combined with scaffolding using published data provided a quality comparable to published assemblies for \textit{Mytilus} species.

@@

We thank [XXX].
AS was supported by the ANR grant [XXX] and by the National Institute of General Medical Sciences of the National Institutes of Health (grants NIH R01 GM108779 and R35 GM136290 to Dr Graham Coop).
